Effectiveness of BNT162b2 booster doses in England: a observational study in OpenSAFELY-TPP: Materials

### 2022-03-23 manuscript/reports.Rmd
updates

cohortsummary <- read_csv(fs::path(output_dir_os, "cohortsummary.csv"))
matchsummary <- read_csv(fs::path(output_dir_os, "matchsummary.csv"))
matchsummary_treated <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 1L)
matchsummary_control <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 0L)
matchflowchart <- read_csv(fs::path(output_dir_os, "matchflowchart.csv"))
matchcoverage <- read_csv(fs::path(output_dir_os, "matchcoverage.csv"))
incidences <- read_csv(fs::path(output_dir_os, "none", "incidence_all.csv")) %>% mutate(events=events_1+events_0)

studydurationweeks <- as.numeric(as.duration(study_dates$studyend_date - study_dates$studystart_date +1) , "weeks")
```

@@

km <- 
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "km.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "km.csv")),
    read_csv(fs::path(output_dir_os, "cev", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level))
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level = fct_inorder(subgroup_level),
    subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=12)),
    #model_name = fct_inorder(str_wrap(model_name, 15)),
  )
# 
# cmlinc <- read_csv(fs::path(output_dir_os, "cmlinc.csv")) %>%
#   mutate(
#     treatment_descr = fct_inorder(treatment_descr),
#     outcome_descr = fct_inorder(outcome_descr),
#     model_name = fct_inorder(str_wrap(model_name, 15)),
#     inc_CI_to = paste0(label_number(0.1, scale=1000)(1-survival.ul), " to ", label_number(0.1, scale=1000)(1-survival.ll))
#   )

@@

meta28hazards <- 
  # derive directly from hazards as meta28effects table needs to be re-run
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "effects.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "effects.csv")),
    read_csv(fs::path(output_dir_os, "cev", "effects.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(
    period = (term_right>28) + 1,
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level = fct_inorder(subgroup_level),
    subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=15)),
  ) %>%
  group_by(
    treatment, treatment_descr, outcome, outcome_descr, outcome_descr_wrap, subgroup, subgroup_variable, subgroup_descr, subgroup_level, subgroup_level_descr, model, model_descr, period, 
  ) %>%
  summarise(
    term_left = min(term_left),
    term_right = max(term_right),
    term_midpoint = (term_left+term_right)/2,
    estimate = weighted.mean(estimate, robust.se^-2),
    std.error = sqrt(1/sum(std.error^-2)),
    robust.se = sqrt(1/sum(robust.se^-2)),
    statistic = estimate/robust.se,
    p.value = 2 * pmin(pnorm(statistic), pnorm(-statistic)),
    conf.low = estimate + qnorm(0.025)*robust.se,
    conf.high = estimate + qnorm(0.975)*robust.se,
    hr = exp(estimate),
    hr.ll = exp(conf.low),
    hr.ul = exp(conf.high),
    ve = 1-hr,
    ve.ll = 1-hr.ul,
    ve.ul = 1-hr.ll
  ) %>%
  ungroup() %>%
  mutate(
    hr_display = paste0(label_number(accuracy=0.01)(hr), " (", label_number(accuracy=0.01)(hr.ll), "-", label_number(accuracy=0.01)(hr.ul), ")"),
    ve_display = paste0(label_percent(accuracy=0.1)(ve), " (", label_percent(accuracy=0.1, suffix="")(ve.ll), "-", label_percent(accuracy=0.1, suffix="")(ve.ul), ")"),
  )

meta42hazards <- 
  # derive directly from hazards as meta28effects table needs to be re-run
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "effects.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "effects.csv")),
    read_csv(fs::path(output_dir_os, "cev", "effects.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(
    period = (term_right>42) + 1,
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level = fct_inorder(subgroup_level),
    subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=15)),
  ) %>%
  group_by(
    treatment, treatment_descr, outcome, outcome_descr, outcome_descr_wrap, subgroup, subgroup_variable, subgroup_descr, subgroup_level, subgroup_level_descr, model, model_descr, period, 
  ) %>%
  summarise(
    term_left = min(term_left),
    term_right = max(term_right),
    term_midpoint = (term_left+term_right)/2,
    estimate = weighted.mean(estimate, robust.se^-2),
    std.error = sqrt(1/sum(std.error^-2)),
    robust.se = sqrt(1/sum(robust.se^-2)),
    statistic = estimate/robust.se,
    p.value = 2 * pmin(pnorm(statistic), pnorm(-statistic)),
    conf.low = estimate + qnorm(0.025)*robust.se,
    conf.high = estimate + qnorm(0.975)*robust.se,
    hr = exp(estimate),
    hr.ll = exp(conf.low),
    hr.ul = exp(conf.high),
    ve = 1-hr,
    ve.ll = 1-hr.ul,
    ve.ul = 1-hr.ll
  ) %>%
  ungroup() %>%
  mutate(
    hr_display = paste0(label_number(accuracy=0.01)(hr), " (", label_number(accuracy=0.01)(hr.ll), "-", label_number(accuracy=0.01)(hr.ul), ")"),
    ve_display = paste0(label_percent(accuracy=0.1)(ve), " (", label_percent(accuracy=0.1, suffix="")(ve.ll), "-", label_percent(accuracy=0.1, suffix="")(ve.ul), ")"),
  )

@@

#### Table 1: Participant characteristics

@@

@@

#### Table 2: Follow-up and outcomes

Total follow-up and incidence rates for each outcome, by treatment group. The cumulative incidence of each outcome is provided in Supplementary Figure S2.

```{r table2, echo=FALSE, warning=FALSE, message=FALSE}
incidences %>%
  filter(
    fup_period == "All",
    outcome %in% c("postest", "covidadmitted", "coviddeath"),
    treatment == "pfizer"
  ) %>%
  left_join(
    matchsummary %>% select(treatment, n_eligible, prop_matched_eligible),
    by=c("treatment")
  ) %>%
  mutate(
    treatment_descr = paste0(
      #treatment_descr, " - ",
      label_number(1, big.mark=",")(n_eligible), " eligible, ",
      label_number(1, big.mark=",")(n_1), " matched (",
      label_percent(0.1)(prop_matched_eligible), ")."
    ),
  ) %>%
  select(
    treatment_descr, 
    outcome_descr,
    q_1,
    rate_1,
    q_0, 
    rate_0,
    rrECI
  ) %>%
  mutate(
    rate_1=if_else(rate_1<0.001, "<0.001", label_number(0.001)(rate_1)),
    rate_0=if_else(rate_0<0.001, "<0.001", label_number(0.001)(rate_0)),
  ) %>%
  gt(
   groupname_col = c("treatment_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    outcome_descr = "Outcome",

@@

## Table 3a: Estimated booster effectiveness (5 period)

@@

hazards %>%
  filter(model==3, treatment=="pfizer") %>%
  mutate(
    period = paste(term_left+1, "-", term_right),
    ve_display = str_remove(ve_display, fixed("%"))
  ) %>%
  arrange(treatment_descr, outcome_descr, subgroup_level_descr, term_left) %>%
  group_by(outcome, treatment, subgroup_level_descr, model) %>%
  mutate(
    subgroup_level_descr=if_else(row_number()==1, subgroup_level_descr, factor(NA, levels=levels(subgroup_level_descr)))
  ) %>%
  ungroup() %>%
  select(outcome_descr, subgroup_level_descr, period, hr_display, ve_display) %>%
  gt(
    groupname_col = c("outcome_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    subgroup_level_descr="",
    outcome_descr = "Outcome",

    period = "Days since booster",
    hr_display   = "HR (95% CI)",
    ve_display   = "VE (95% CI)",
  ) %>%
  cols_align(
    align = "right",
    columns = everything()
  ) %>%
  fmt_missing(
    c("subgroup_level_descr"),
    missing_text=""
  )

@@

## Table 3b: Estimated booster effectiveness (2 period split at 28 days)

```{r table_effects28, echo=FALSE, message=FALSE, warning=FALSE, out.extra='', fig.height=7.5, out.width='90%', results='asis'}

meta28hazards %>%
  filter(model==3, treatment=="pfizer") %>%
  mutate(
    period = paste(term_left+1, "-", term_right),
    ve_display = str_remove(ve_display, fixed("%"))
  ) %>%
  arrange(treatment_descr, outcome_descr, subgroup_level_descr, term_left) %>%
  group_by(outcome, treatment, subgroup_level_descr, model) %>%
  mutate(
    subgroup_level_descr=if_else(row_number()==1, subgroup_level_descr, factor(NA, levels=levels(subgroup_level_descr)))
  ) %>%
  ungroup() %>%
  select(outcome_descr, subgroup_level_descr, period, hr_display, ve_display) %>%
  gt(
    groupname_col = c("outcome_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    subgroup_level_descr="",
    outcome_descr = "Outcome",

    period = "Days since booster",
    hr_display   = "HR (95% CI)",
    ve_display   = "VE (95% CI)",
  ) %>%
  cols_align(
    align = "right",
    columns = everything()
  ) %>%
  fmt_missing(
    c("subgroup_level_descr"),
    missing_text=""
  )

## Table 3c: Estimated booster effectiveness (2 period split at 42 days)

```{r table_effects42, echo=FALSE, message=FALSE, warning=FALSE, out.extra='', fig.height=7.5, out.width='90%', results='asis'}

meta28hazards %>%
  filter(model==3, treatment=="pfizer") %>%
  mutate(
    period = paste(term_left+1, "-", term_right),
    ve_display = str_remove(ve_display, fixed("%"))
  ) %>%
  arrange(treatment_descr, outcome_descr, subgroup_level_descr, term_left) %>%
  group_by(outcome, treatment, subgroup_level_descr, model) %>%
  mutate(
    subgroup_level_descr=if_else(row_number()==1, subgroup_level_descr, factor(NA, levels=levels(subgroup_level_descr)))
  ) %>%
  ungroup() %>%
  select(outcome_descr, subgroup_level_descr, period, hr_display, ve_display) %>%
  gt(
    groupname_col = c("outcome_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    subgroup_level_descr="",
    outcome_descr = "Outcome",

    period = "Days since booster",
    hr_display   = "HR (95% CI)",
    ve_display   = "VE (95% CI)",
  ) %>%
  cols_align(
    align = "right",
    columns = everything()
  ) %>%
  fmt_missing(
    c("subgroup_level_descr"),
    missing_text=""
  )

@@

xmin <- min(matchcoverage$vax3_date )
xmax <- max(matchcoverage$vax3_date )+1
data_coverage <- matchcoverage  %>%
  mutate(
    status = factor(status, levels=c("ineligible", "unmatched", "matched")),
    status_descr = fct_relabel(status, str_to_title)
  ) %>%
  arrange(status) %>%
  mutate(
    status_descr = fct_inorder(status_descr)
  ) %>%
  filter(treatment=="pfizer") %>%
  mutate(
    # vax12_type = fct_case_when(
    #   vax12_type == "pfizer-pfizer" ~ "BNT162b2",
    #   vax12_type == "az-az" ~ "ChAdOx1-S",
    #   vax12_type == "moderna-moderna" ~ "mRNA-1273",
    #   TRUE ~ NA_character_
    # ),
    course = fct_case_when(
      vax12_type=="pfizer-pfizer" & treatment=="pfizer" ~ "2× BNT162b2  / 1× BNT162b2",
      vax12_type=="az-az" & treatment=="pfizer" ~ "2× ChAdOx1-S / 1× BNT162b2",
      vax12_type=="pfizer-pfizer" & treatment=="moderna" ~ "2× BNT162b2 / 1× mRNA-1273",
      vax12_type=="az-az" & treatment=="moderna" ~ "2× ChAdOx1-S / 1× mRNA-1273",
      TRUE ~ NA_character_
    )
  )

>>>>

cohortsummary <- read_csv(fs::path(output_dir_os, "cohortsummary.csv"))
matchsummary <- read_csv(fs::path(output_dir_os, "matchsummary.csv"))
matchsummary_treated <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 1L)
matchsummary_control <- read_csv(fs::path(output_dir_os, "matchsummary_treated.csv")) %>% filter(treated == 0L)
matchflowchart <- read_csv(fs::path(output_dir_os, "matchflowchart.csv"))
matchcoverage <- read_csv(fs::path(output_dir_os, "matchcoverage.csv"))
incidences <- read_csv(fs::path(output_dir_os, "none", "incidence.csv")) %>% mutate(events=events_1+events_0)

@@

km <- 
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "km.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "km.csv")),
    read_csv(fs::path(output_dir_os, "cev", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "prior_covid_infection", "km.csv")) %>% mutate(subgroup_level=as.character(subgroup_level))
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level = fct_inorder(subgroup_level),
    subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=12)),
    #model_name = fct_inorder(str_wrap(model_name, 15)),
  )
# 
# cmlinc <- read_csv(fs::path(output_dir_os, "cmlinc.csv")) %>%
#   mutate(
#     treatment_descr = fct_inorder(treatment_descr),
#     outcome_descr = fct_inorder(outcome_descr),
#     model_name = fct_inorder(str_wrap(model_name, 15)),
#     inc_CI_to = paste0(label_number(0.1, scale=1000)(1-survival.ul), " to ", label_number(0.1, scale=1000)(1-survival.ll))
#   )

@@

meta28hazards <- 
  # derive directly from hazards as meta28effects table needs to be re-run
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "effects.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "effects.csv")),
    read_csv(fs::path(output_dir_os, "cev", "effects.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "prior_covid_infection", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(
    period = (term_right>28) + 1,
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level = fct_inorder(subgroup_level),
    subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=15)),
  ) %>%
  group_by(
    treatment, treatment_descr, outcome, outcome_descr, outcome_descr_wrap, subgroup, subgroup_variable, subgroup_descr, subgroup_level, subgroup_level_descr, model, model_descr, period, 
  ) %>%
  summarise(
    term_left = min(term_left),
    term_right = max(term_right),
    term_midpoint = (term_left+term_right)/2,
    estimate = weighted.mean(estimate, robust.se^-2),
    std.error = sqrt(1/sum(std.error^-2)),
    robust.se = sqrt(1/sum(robust.se^-2)),
    statistic = estimate/robust.se,
    p.value = 2 * pmin(pnorm(statistic), pnorm(-statistic)),
    conf.low = estimate + qnorm(0.025)*robust.se,
    conf.high = estimate + qnorm(0.975)*robust.se,
    hr = exp(estimate),
    hr.ll = exp(conf.low),
    hr.ul = exp(conf.high),
    ve = 1-hr,
    ve.ll = 1-hr.ul,
    ve.ul = 1-hr.ll
  ) %>%
  ungroup() %>%
  mutate(
    hr_display = paste0(label_number(accuracy=0.01)(hr), " (", label_number(accuracy=0.01)(hr.ll), "-", label_number(accuracy=0.01)(hr.ul), ")"),
    ve_display = paste0(label_percent(accuracy=0.1)(ve), " (", label_percent(accuracy=0.1, suffix="")(ve.ll), "-", label_percent(accuracy=0.1, suffix="")(ve.ul), ")"),
  )

meta42hazards <- 
  # derive directly from hazards as meta28effects table needs to be re-run
  bind_rows(
    read_csv(fs::path(output_dir_os, "none", "effects.csv")),
    read_csv(fs::path(output_dir_os, "vax12_type", "effects.csv")),
    read_csv(fs::path(output_dir_os, "cev", "effects.csv")) %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "age65plus", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
    read_csv(fs::path(output_dir_os, "prior_covid_infection", "effects.csv"))  %>% mutate(subgroup_level=as.character(subgroup_level)),
  ) %>%
  filter(
    outcome %in% outcomes
  ) %>%
  mutate(
    period = (term_right>42) + 1,
    subgroup_descr = fct_inorder(subgroup_descr),
    subgroup_level = fct_inorder(subgroup_level),
    subgroup_level_descr = fct_inorder(fct_explicit_na(subgroup_level_descr, "All")),
    treatment_descr = fct_inorder(treatment_descr),
    outcome_descr = fct_inorder(outcome_descr),
    outcome_descr_wrap = fct_relabel(outcome_descr, ~str_wrap(., width=15)),
  ) %>%
  group_by(
    treatment, treatment_descr, outcome, outcome_descr, outcome_descr_wrap, subgroup, subgroup_variable, subgroup_descr, subgroup_level, subgroup_level_descr, model, model_descr, period, 
  ) %>%
  summarise(
    term_left = min(term_left),
    term_right = max(term_right),
    term_midpoint = (term_left+term_right)/2,
    estimate = weighted.mean(estimate, robust.se^-2),
    std.error = sqrt(1/sum(std.error^-2)),
    robust.se = sqrt(1/sum(robust.se^-2)),
    statistic = estimate/robust.se,
    p.value = 2 * pmin(pnorm(statistic), pnorm(-statistic)),
    conf.low = estimate + qnorm(0.025)*robust.se,
    conf.high = estimate + qnorm(0.975)*robust.se,
    hr = exp(estimate),
    hr.ll = exp(conf.low),
    hr.ul = exp(conf.high),
    ve = 1-hr,
    ve.ll = 1-hr.ul,
    ve.ul = 1-hr.ll
  ) %>%
  ungroup() %>%
  mutate(
    hr_display = paste0(label_number(accuracy=0.01)(hr), " (", label_number(accuracy=0.01)(hr.ll), "-", label_number(accuracy=0.01)(hr.ul), ")"),
    ve_display = paste0(label_percent(accuracy=0.1)(ve), " (", label_percent(accuracy=0.1, suffix="")(ve.ll), "-", label_percent(accuracy=0.1, suffix="")(ve.ul), ")"),
  )

@@

#### Table 1a: Participant characteristics for Pfizer boosting

@@

#### Table 1b: Participant characteristics for Moderna boosting

```{r table1, echo=FALSE, warning=FALSE, message=FALSE}
table1_body <- read_csv(fs::path(output_dir_os, "matchtable1.csv")) %>% filter(treatment=="moderna")
table1_by <- read_csv(fs::path(output_dir_os, "matchtable1by.csv")) %>% filter(treatment=="moderna")

@@

#### Table 2a: Follow-up and outcomes for Pfizer boosting

Total follow-up and incidence rates for each outcome, by treatment group.

```{r table2, echo=FALSE, warning=FALSE, message=FALSE}
incidences %>%
  filter(
    fup_period == "All",
    outcome %in% c("postest", "covidadmitted", "coviddeath", "noncoviddeath"),
    treatment == "pfizer"
  ) %>%
  left_join(
    matchsummary %>% select(treatment, n_eligible, prop_matched_eligible),
    by=c("treatment")
  ) %>%
  mutate(
    treatment_descr = paste0(
      #treatment_descr, " - ",
      label_number(1, big.mark=",")(n_eligible), " eligible, ",
      label_number(1, big.mark=",")(n_1), " matched (",
      label_percent(0.1)(prop_matched_eligible), ")."
    ),
  ) %>%
  select(
    treatment_descr, 
    outcome_descr,
    q_1,
    rate_1,
    q_0, 
    rate_0,
    rrECI
  ) %>%
  mutate(
    rate_1=if_else(rate_1<0.001, "<0.001", label_number(0.001)(rate_1)),
    rate_0=if_else(rate_0<0.001, "<0.001", label_number(0.001)(rate_0)),
  ) %>%
  gt(
   groupname_col = c("treatment_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    outcome_descr = "Outcome",

@@

#### Table 2b: Follow-up and outcomes for Moderna boosting

Total follow-up and incidence rates for each outcome, by treatment group.

```{r table2, echo=FALSE, warning=FALSE, message=FALSE}
incidences %>%
  filter(
    fup_period == "All",
    outcome %in% c("postest", "covidadmitted", "coviddeath", "noncoviddeath"),
    treatment == "moderna"
  ) %>%
  left_join(
    matchsummary %>% select(treatment, n_eligible, prop_matched_eligible),
    by=c("treatment")
  ) %>%
  mutate(
    treatment_descr = paste0(
      #treatment_descr, " - ",
      label_number(1, big.mark=",")(n_eligible), " eligible, ",
      label_number(1, big.mark=",")(n_1), " matched (",
      label_percent(0.1)(prop_matched_eligible), ")."
    ),
  ) %>%
  select(
    treatment_descr, 
    outcome_descr,
    q_1,
    rate_1,
    q_0, 
    rate_0,
    rrECI
  ) %>%
  mutate(
    rate_1=if_else(rate_1<0.001, "<0.001", label_number(0.001)(rate_1)),
    rate_0=if_else(rate_0<0.001, "<0.001", label_number(0.001)(rate_0)),
  ) %>%
  gt(
   groupname_col = c("treatment_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    outcome_descr = "Outcome",

## Table 3a: Estimated Pfizer booster effectiveness (5 period)

@@

bind_rows(
  hazards,
  overallhazards %>% mutate(term_left = 0, term_right=70)
) %>%
  filter(model==3, treatment=="pfizer") %>%
  mutate(
    period = fct_inorder(paste(term_left+1, "-", term_right)),
    ve_display = str_remove(ve_display, fixed("%"))
  ) %>%
  arrange(treatment_descr, outcome_descr, subgroup_level_descr, period) %>%
  group_by(outcome, treatment, subgroup_level_descr, model) %>%
  mutate(
    #subgroup_level_descr=if_else(row_number()==1, subgroup_level_descr, factor(NA, levels=levels(subgroup_level_descr))),
    period = paste0(period, " days")
  ) %>%
  ungroup() %>%
  select(outcome_descr, subgroup_level_descr, period, ve_display) %>%
  pivot_wider(
    id_cols = c("outcome_descr", "subgroup_level_descr"),
    names_from = "period",
    #names_prefix ="period",
    values_from = "ve_display"
  ) %>%
  gt(
    groupname_col = c("outcome_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    subgroup_level_descr="",
    outcome_descr = "Outcome",
  ) %>%
  cols_align(
    align = "right",
    columns = everything()
  ) %>%
  tab_spanner(
    label = "Booster vaccine effectiveness (95% CI)",
    columns = ends_with("days")
  ) %>%
  fmt_missing(
    c("subgroup_level_descr"),
    missing_text=""
  )

@@

## Table 3a: Estimated Moderna booster effectiveness (5 period)

bind_rows(
  hazards,
  overallhazards %>% mutate(term_left = 0, term_right=70)
) %>%
  filter(model==3, treatment=="moderna") %>%
  mutate(
    period = fct_inorder(paste(term_left+1, "-", term_right)),
    ve_display = str_remove(ve_display, fixed("%"))
  ) %>%
  arrange(treatment_descr, outcome_descr, subgroup_level_descr, period) %>%
  group_by(outcome, treatment, subgroup_level_descr, model) %>%
  mutate(
    #subgroup_level_descr=if_else(row_number()==1, subgroup_level_descr, factor(NA, levels=levels(subgroup_level_descr))),
    period = paste0(period, " days")
  ) %>%
  ungroup() %>%
  select(outcome_descr, subgroup_level_descr, period, ve_display) %>%
  pivot_wider(
    id_cols = c("outcome_descr", "subgroup_level_descr"),
    names_from = "period",
    #names_prefix ="period",
    values_from = "ve_display"
  ) %>%
  gt(
    groupname_col = c("outcome_descr"),
  ) %>%
  cols_label(
    #treatment_descr = "Treatment",
    subgroup_level_descr="",
    outcome_descr = "Outcome",
  ) %>%
  cols_align(
    align = "right",
    columns = everything()
  ) %>%
  tab_spanner(
    label = "Booster vaccine effectiveness (95% CI)",
    columns = ends_with("days")
  ) %>%
  fmt_missing(
    c("subgroup_level_descr"),
    missing_text=""
  )

@@

xmin <- min(matchcoverage$vax3_date )
xmax <- max(matchcoverage$vax3_date )+1
data_coverage <- matchcoverage  %>%
  mutate(
    status = factor(status, levels=c("ineligible", "unmatched", "matched")),
    status_descr = fct_relabel(status, str_to_title)
  ) %>%
  arrange(status) %>%
  mutate(
    status_descr = fct_inorder(status_descr)
  ) %>%
  #filter(treatment=="pfizer") %>%
  mutate(
    # vax12_type = fct_case_when(
    #   vax12_type == "pfizer-pfizer" ~ "BNT162b2",
    #   vax12_type == "az-az" ~ "ChAdOx1-S",
    #   vax12_type == "moderna-moderna" ~ "mRNA-1273",
    #   TRUE ~ NA_character_
    # ),
    course = fct_case_when(
      vax12_type=="pfizer-pfizer" & treatment=="pfizer" ~ "2× BNT162b2  / 1× BNT162b2",
      vax12_type=="az-az" & treatment=="pfizer" ~ "2× ChAdOx1-S / 1× BNT162b2",
      vax12_type=="pfizer-pfizer" & treatment=="moderna" ~ "2× BNT162b2 / 1× mRNA-1273",
      vax12_type=="az-az" & treatment=="moderna" ~ "2× ChAdOx1-S / 1× mRNA-1273",
      TRUE ~ NA_character_
    )
  )
